---
title: "R Notebook"
output: pdf_notebook
---

set directory and read in dataset
```{r}
setwd("..")
```


```{r}
setwd("../test/test_output")
```

```{r}
setwd("..")
```

```{r}
getwd()
```

```{r}
setwd('../test/testdata')
filename = 'test_mootha.txt';
mootha  = read.table(filename)
```

Install the packages if have not been done yet, ignore if have done so

install.packages("psych",dependencies=TRUE)

separate data by its feature, in our case, it's whether diabetes or not
```{r}
g1 = 1:17
g2 = 18:34
s1 = sample(g1, 2, replace=FALSE)
s2 = sample(g2, 2, replace=FALSE)
sm_sample = c(s1,s2)
mootha[,sm_sample]
```
```{r}
library(psych)
```

Function for plotting the matrix
We only include four person's data by randomly choosing from the two groups
```{r}
path = '../test/test_output/corr.png'
png(filename=path)

pairs.panels(mootha[,sm_sample], 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = TRUE # show correlation ellipses
             )

dev.off()
```


```{r}
library(tidyr)
library(dplyr)
```
Here we want to find the summary of the dataset's stats
First use the gather function from tidyr

Then save the stats as a table, including mean, standard deviation, max and min of each person's gene expression
```{r}
mootha_long <- gather(mootha, factor_key=TRUE)

summarydf <- mootha_long %>% group_by(key) %>%
  summarize(mean= mean(value), sd= sd(value), max = max(value),min = min(value))

summarydf
```

```{r}
write.csv(summarydf, '../test/test_output/stats_summary.csv')
```

Redo and find the mean of each stats by groups, save them as a dataframe
```{r}
g1_stat = apply(summarydf[g1,2:5],2,mean)
g2_stat = apply(summarydf[g2,2:5],2,mean)

g1_stat
g2_stat

group_stat = data.frame(g1_stat,g2_stat)
```

```{r}
write.csv(group_stat, '../test/test_output/group_stat.csv')
```



#######2
path_2 = './src/eda.R'
# source that path
source(path_2)

if (length(target) == 0){
  target = "test"
}

# run these functions
if ('eda' %in% target) {
  params = fromJSON(file = "./config/eda-params.json")
  eda_generator(params['data'],params['csv_filename'],params['g1'],params['g2'])
} else if ('all' %in% target) {
  # build path and load data for the first method
  data_fp = fromJSON(file = "./config/methods.json")
  
  path = data_fp['data_fp']
  mootha  = read.table(as.character(path), header = TRUE)
  mootha_function(mootha)
  
  # build path and load data for the second method
  path2 = data_fp['data_fp2']
  Z = scan(as.character(path2))
  Jongho_function(Z)
} else if ('test' %in% target){
  # build path and load data for the first method
  data_fp = fromJSON(file = "./config/test.json")
  
  path = data_fp['data_fp']
  g1 = data_fp['g1']
  g2 = data_fp['g1']
  mootha  = read.table(as.character(path), header = TRUE)
  eda_generator(mootha,g1,g2)
} else {
  print('invalid input. Command Line options -- all/test (default test)')
}




